Evaluating the Performance and Energy Efficiency of COSMO-ART, a Coupled Numerical Weather Forecast and Chemical Transport Model

### 2014-04-12 trunk/paper_enahpc14/Sec3:Measurement-framework.tex
adds minor changes

\subsubsection{E3METER metering products}
Supercomputer  clusters considered  for our  experiments at  the Swiss
National Supercomputing Center of  ETH Zurich (CSCS) are equipped with
E3METER Intelligent  Power Strips (IPS)  and Monitors (IPM)  which are
high   quality   electricity  meters   released   by  Riedo   Networks
(\url{http://riedonetworks.com/}),  that  enable  to monitor  and  log
power  consumption of  the  IT infrastructure  as  well as  constantly
analyze  line  voltage,  current,  power-factor,  frequency  with  1\%
accuracy.   Using reliable  narrowband  powerline communication  (PLC)
technology,  all metering  and power  quality data  from each  IPS are
centrally collected by the E3METER Data Concentrator, via the existing
power cables thus  avoiding the need for extra  cabling.  This data is
made  available  via SNMP,  HTTP,  TELNET  through  the built-in  Fast
Ethernet  port.   Time  synchronization  is guaranteed  by  using  NTP
servers.   Measured data  is accessed  through the  open  source Cacti
software including  the E3METER  Cacti Plugin to  scan the  entire PLC
network and monitor the power usage of individual rack in real-time.

>>>>

\subsubsection{E3METER metering products}
Supercomputer  clusters considered  for our  experiments at  the Swiss
National Supercomputing Center of  ETH Zurich (CSCS) are equipped with
E3METER Intelligent  Power Strips (IPS)  and Monitors (IPM)  which are
high   quality   electricity  meters   released   by  Riedo   Networks
(\url{http://riedonetworks.com/}),  that  enable  to monitor  and  log
power  consumption of  the  IT infrastructure  as  well as  constantly
analyze  line  voltage,  current,  power-factor,  frequency  with  1\%
accuracy.   Using reliable  narrowband  powerline communication  (PLC)
technology,  all metering  and power  quality data  from each  IPS are
centrally collected by the E3METER Data Concentrator, via the existing
power cables thus  avoiding the need for extra  cabling.  This data is
made  available  via SNMP,  HTTP,  TELNET  through  the built-in  Fast
Ethernet  port.   Time  synchronization  is guaranteed  by  using  NTP
servers.   Measured data  is accessed  through the  open  source Cacti
software including  the E3METER  Cacti Plugin to  scan the  entire PLC
network and monitor  in real-time the power usage  of individual rack,
recorded in 5 minutes interval periods.

### 2014-04-12 trunk/paper_enahpc14/Sec4:Evaluation.tex
adds minor changes

\subsubsection{Sofware environment}
INT2LM  and the  COSMO-ART model  are  implemented in  Fortran 90  for
distributed  memory  parallel  computers  using  the  Message  Passing
Interface (MPI)  and are purely  MPI-parallel.  The software  stack on
both many-core  platforms was  controlled using the  modules framework
which gives  an easy and  flexible mechanism to  access to all  of the
CSCS  provided compilers,  tools  and applications.   For our  initial
benchmarking,  we opted  for  the GNU  compiler  (gcc/4.8.1 on  Monch,
gcc/4.8.2 on Pilatus) with the -O3 compiler flag as it generally gives
a  good  level  of optimization  and  the  code  runs faster  in  this
configuration  than when  compiled with  the intel  compiler (14.0.1).
Besides, we installed the  MPICH2 implementation of MPI (mvapich2/1.9)
as  well  as  the  commonly  used HDF5  (1.8.12)  and  NetCDF  (4.3.1)
libraries in favor of the  traditional GRIB library for the management
of extremely  large and complex data collections.   All computes nodes
have    an   operating   system    based   on    GNU/Linux   featuring
``2.6.32-358.11.1.el6.x86\_64''  and  ``3.0.101-0.15-default'' kernels
for Monch and Pilatus respectively.

>>>>

\subsubsection{Sofware environment}
INT2LM  and the  COSMO-ART model  are  implemented in  Fortran 90  for
distributed  memory  parallel  computers  using  the  Message  Passing
Interface (MPI)  and are purely  MPI-parallel.  The software  stack on
both many-core  platforms was  controlled using the  modules framework
which gives  an easy and  flexible mechanism to  access to all  of the
CSCS  provided compilers,  tools  and applications.   For our  initial
benchmarking,  we opted  for  the GNU  compiler  (gcc/4.8.1 on  Monch,
gcc/4.8.2 on Pilatus) with the -O3 compiler flag as it generally gives
a  good  level  of optimization  and  the  code  runs faster  in  this
configuration  than when  compiled with  the intel  compiler (14.0.1).
Besides, we installed the  MPICH2 implementation of MPI (mvapich2/1.9)
as  well  as  the  commonly  used HDF5  (1.8.12)  and  NetCDF  (4.3.1)
libraries in favor of the  traditional GRIB library for the management
of extremely  large and complex data collections.   All computes nodes
have    an   operating   system    based   on    GNU/Linux   featuring
``2.6.32-358.11.1.el6.x86\_64''      kernel      in     Monch      and
``3.0.101-0.15-default'' kernel in Pilatus.
